---
title: "Untitled"
author: "Matthew Wilson"
date: "2023-02-21"
output: html_document
always_allow_html: true
---

```{r setup, include=FALSE}
# set code chunk options to disable echo by default
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

## test info box as div

```{r test_box_border }

mumhquarterly::infoBox_border("This is box 1",
                              text = "This is some text that might look like 2 million items in 2020/21")

```

placed in a proper div this code doesn't seem to be recognised as HTML. probably some setting to tweak to make this work

## test info box in-line

`r mumhquarterly::infoBox_border("This is box 2", text = "This is some more text that might say 2 million items")`

## testing multi-column layout

### `style="display: flex;"`

This flex layout has width of info box set to 100%.

::::{style="display: flex;"}

:::{}
`r mumhquarterly::infoBox_border("This is box 3", text = "this text goes on the left", width = "100%")`
:::

:::{}
`r mumhquarterly::infoBox_border("This is box 4", text = "this text goes on the right", width = "100%")`
:::

::::

### `style="display: grid;"`

::::{style="display: grid;"}

:::{}
`r mumhquarterly::infoBox_border("This is box 5", text = "this text goes on the left")`
:::

:::{}
`r mumhquarterly::infoBox_border("This is box 6", text = "this text goes on the right")`
:::

::::

### in-line

`r mumhquarterly::infoBox_border("This is box 7", text = "this text goes on the left")` `r mumhquarterly::infoBox_border("This is box 8", text = "this text goes on the left")`

### in-line with 50% width
`r mumhquarterly::infoBox_border("This is box 7", text = "this text goes on the left", width = "50%")` `r mumhquarterly::infoBox_border("This is box 8", text = "this text goes on the left", width = "50%")`

## testing info box no border

```{r test_box_no_border }

mumhquarterly::infoBox_no_border("This is box 8",
                              text = "This is some text that might look like 2 million items in 2020/21")

```

placed in a proper div this code doesn't seem to be recognised as HTML. probably some setting to tweak to make this work

## test info box in-line

`r mumhquarterly::infoBox_no_border("This is box 9", text = "This is some more text that might say 2 million items")`

## testing multi-column layout

### `style="display: flex;"`

This flex layout has width of info box set to 100%.

::::{style="display: flex;"}

:::{}
`r mumhquarterly::infoBox_no_border("This is box 10", text = "this text goes on the left", width = "100%")`
:::

:::{}
`r mumhquarterly::infoBox_no_border("This is box 11", text = "this text goes on the right", width = "100%")`
:::

::::

### `style="display: grid;"`

::::{style="display: grid;"}

:::{}
`r mumhquarterly::infoBox_no_border("This is box 12", text = "this text goes on the left")`
:::

:::{}
`r mumhquarterly::infoBox_no_border("This is box 13", text = "this text goes on the right")`
:::

::::

### in-line

`r mumhquarterly::infoBox_no_border("This is box 14", text = "this text goes on the left")` `r mumhquarterly::infoBox_no_border("This is box 15", text = "this text goes on the left")`

### in-line with 49% width
`r mumhquarterly::infoBox_no_border("This is box 14", text = "this text goes on the left", width = "49%")` `r mumhquarterly::infoBox_no_border("This is box 15", text = "this text goes on the left", width = "49%")`

