---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mumhquarterly

<!-- badges: start -->
<!-- badges: end -->

This code is published as part of the NHSBSA Official Statistics team's commitment to open code and transparency in how we produce our publications. The mumhquarterly package is owned and maintained by the Official Statistics team.

# Introduction

The goal of mumhquarterly is to bring together all of the functions required for production of the [Medicines Used in Mental Health quarterly Official Statistics publication](https://www.nhsbsa.nhs.uk/statistical-collections/medicines-used-mental-health-england) by the NHSBSA with accompanying documentation in line with reproducible analytical pipeline (RAP) best practice. These functions are designed to be used as part of the [MUMH quarterly RAP](https://github.com/nhsbsa-data-analytics/mumh-quarterly-rap), also available on GitHub.

This package is a work in progress and will be replaced by several new packages designed to hold functions used in the creation of our Official Statistics publications. The current mumhquarterly package does not contain unit testing, and this will not be added due to the move to the new packages.

## Installation

You can install the development version of mumhquarterly from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nhsbsa-data-analytics/mumhquarterly")
```
You can also view the [source code for the mumhquarterly package](https://github.com/nhsbsa-data-analytics/mumhquarterly) on GitHub.

# 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(mumhquarterly)
## basic example code
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.

# Contributing

Contributions are not currently being accepted for the mumhquarterly package. If this changes, a contributing guide will be made available.

# License

The mumhquarterly package repository, including associated documentation, is released under the MIT license. Details can be found in the `LICENSE` file.
